### 2017-05-21 presentations/na_cool_paper/sequence.tex
[presentations/na_cool_paper] better sequence plot

    %% Axial
    \foreach \i in {0,...,7} {
      \fill[blue!30]
      plot[draw,samples=200,domain={2.8*\i}:{2.8*\i+1.6},variable=\x] ({\x}, {sin((\x-2.8*\i) * 112.5)^4})
      -- cycle;
      \draw[line width=1,blue] plot[domain={2.8*\i}:{2.8*\i+1.6},variable=\x]
      ({\x}, {sin((\x-2.8*\i) * 112.5)^4}) -- (2.8*\i + 2.8, 0);
    }
    \foreach \i in {0,...,3} {
      \path (5.6*\i + 0.8, 1) node[above,blue,align=center] {$n$-th\\order};
      \path (5.6*\i + 3.6, 1) node[above,blue,align=center] {$(n-1)$-th\\order};
    }

@@

    %% OP
    \foreach \i in {0,...,7} {
      \filldraw[fill=orange!30,draw=orange,line width=1.2]
      (2.8*\i+1.58, -6) rectangle (2.8*\i+1.91, -4.5);
      \filldraw[fill=orange!30,draw=orange,line width=1.2]
      (2.8*\i+2.48, -6) rectangle (2.8*\i+2.81, -4.5);
    }
    \draw[line width=2,orange] (0,-6) -- (22.4,-6);

    \fill[white,path fading=fade img right] (16.8, -7) rectangle (17.81, 4);
    \fill[white,path fading=fade img right] (16.8, -7) rectangle (17.81, 4);
    \fill[white,path fading=fade img right] (16.8, -7) rectangle (17.81, 4);

    \fill[white,path fading=fade img left] (5.6, -7) rectangle (4.59, 4);
    \fill[white,path fading=fade img left] (5.6, -7) rectangle (4.59, 4);
    \fill[white,path fading=fade img left] (5.6, -7) rectangle (4.59, 4);
  \end{scope}

  \path (4.95, 2.3) node[left,purple,align=center] {\textbf{Tweezer}};
  \path (4.8, 0.5) node[left,blue,align=center] {\textbf{Axis 1}\\\textit{Axial}};
  \path (4.8, -1.5) node[left,red,align=center] {\textbf{Axis 2}\\\textit{Radial}};
  \path (4.8, -3.5) node[left,black,align=center] {\textbf{Axis 3}\\\textit{Radial}};
  \path (5.1, -5.5) node[left,orange,align=center] {\textbf{Optical}\\\textbf{pumping}};
  \draw[line width=2,orange,->] (5.6,-6) -- (17.8,-6) node[right, below] {\scalebox{2}{$t$}};

>>>>

    %% Axial
    \foreach \i in {0,...,7} {
      \fill[blue!30]
      plot[draw,samples=200,domain={2.8*\i}:{2.8*\i+1.6},variable=\x] ({\x}, {sin((\x-2.8*\i) * 112.5)^4})
      -- cycle;
      \draw[line width=1,blue] plot[domain={2.8*\i}:{2.8*\i+1.6},variable=\x]
      ({\x}, {sin((\x-2.8*\i) * 112.5)^4}) -- (2.8*\i + 2.8, 0);
    }
    \foreach \i in {0,...,3} {
      \path (5.6*\i + 0.8, 1) node[above,blue,align=center] {\textbf{$n$-th}\\\textbf{order}};
      \path (5.6*\i + 3.6, 1) node[above,blue,align=center] {\textbf{$(n-1)$-th}\\\textbf{order}};
    }

@@

    %% OP
    \foreach \i in {0,...,7} {
      \filldraw[fill=orange!30,draw=orange,line width=1.2]
      (2.8*\i+1.58, -6) rectangle (2.8*\i+1.91, -4.5);
      \filldraw[fill=orange!30,draw=orange,line width=1.2]
      (2.8*\i+2.48, -6) rectangle (2.8*\i+2.81, -4.5);
    }
    \draw[line width=2,orange] (0,-6) -- (22.4,-6);
  \end{scope}

  \fill[white,path fading=fade img right] (16.8, -6.6) rectangle (17.81, 3.51);
  \fill[white,path fading=fade img right] (16.8, -6.6) rectangle (17.81, 3.51);
  \fill[white,path fading=fade img right] (16.8, -6.6) rectangle (17.81, 3.51);

  \fill[white,path fading=fade img left] (5.6, -6.6) rectangle (4.59, 3.51);
  \fill[white,path fading=fade img left] (5.6, -6.6) rectangle (4.59, 3.51);
  \fill[white,path fading=fade img left] (5.6, -6.6) rectangle (4.59, 3.51);

  \path (5.0, 2.3) node[left,purple,align=center] {\textbf{Tweezer}};
  \path (4.8, 0.5) node[left,blue,align=center] {\textbf{Axis 1}\\\textit{Axial}};
  \path (4.8, -1.5) node[left,red,align=center] {\textbf{Axis 2}\\\textit{Radial}};
  \path (4.8, -3.5) node[left,black,align=center] {\textbf{Axis 3}\\\textit{Radial}};
  \path (5.15, -5.5) node[left,orange,align=center] {\textbf{Optical}\\\textbf{pumping}};
  \draw[line width=2,orange,->] (5.6,-6) -- (17.8,-6) node[right, below] {\scalebox{2}{$t$}};
